**Machine learning identifies unique taxa differentiating proximal and distal

### 2017-06-13 submission/manuscript.Rmd
added chunks to manuscript

---
title: '**Machine learning identifies unique taxa differentiating proximal and distal
  human colonic microbiota**'
csl: mbio.csl
fontsize: 11pt
output:
  word_document: default
  pdf_document:
    includes: null
    keep_tex: yes
  html_document: default
geometry: margin=1.0in
bibliography: references.bib
---
\vspace{35mm}

@@

\newpage
\linenumbers

>>>>

---
title: '**Machine learning identifies unique taxa differentiating proximal and distal
  human colonic microbiota*'
csl: mbio.csl
fontsize: 11pt
output:
  word_document: default
  pdf_document:
    includes: null
    keep_tex: yes
  html_document: default
geometry: margin=1.0in
bibliography: references.bib
---
\vspace{35mm}

@@

\newpage
\linenumbers
```{r dependencies}
pack_used <- c('randomForest','ggplot2', 'pROC', 'knitr','dplyr','AUCRF', 'tidyr', 'caret', 'RColorBrewer', 'reshape2', 'wesanderson')
for (dep in pack_used){
  if (dep %in% installed.packages()[,"Package"] == FALSE){
    install.packages(as.character(dep), repos = 'http://cran.us.r-project.org', 
                     quiet=TRUE);
  }
  library(dep, verbose=FALSE, character.only=TRUE)
}
```

```{r datasets}
meta <- 'data/raw/kws_metadata.tsv'
shared <- 'data/mothur/kws_final.an.shared'
tax <- 'data/mothur/kws_final.an.cons.taxonomy'
subsample <- 'data/mothur/kws_final.an.0.03.subsample.shared'

meta_file <- read.table(file='data/raw/kws_metadata.tsv', header = T)
shared_file <- read.table(file='data/mothur/kws_final.an.shared', sep = '\t', header=T, row.names=2)
tax_file <- read.table(file='data/mothur/kws_final.an.cons.taxonomy', sep = '\t', header=T, row.names=1)
shared_meta <- merge(meta_file, shared_file, by.x='group', by.y='row.names')

simps <- read.table(file='data/mothur/kws_final.an.groups.summary', header = T)
metasimp <- merge(metadata, simps)

```

```{r otu_barplot}
source('code/Sum_OTU_by_Tax.R')
source('code/sum_shared.R')

#use this code to assign phyla to each OTU in the shared file 
shared_phyla <- get_tax_level_shared(subsample, tax, 2)
phyla_met <- merge(meta_file, shared_phyla, by.x='group', by.y='row.names')

#try to get the df organized to work as a boxplot - no median calculation 
phyla_test <- phyla_met[, c("location","Firmicutes","Bacteroidetes","Proteobacteria","Verrucomicrobia","Actinobacteria","Fusobacteria")]
subsampled_to <- 4231
RA <- function(x) 100*x/subsampled_to

phyla_RA <- data.frame(phyla_test[1], apply(phyla_test[2:ncol(phyla_test)],2, RA))
phylaRAnames <- colnames(phyla_RA[,1:7])
phyla_RAmelt <- melt(phyla_RA[, phylaRAnames], id.vars=1)

```

```{r simpson}

```
